A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-07 03_Prep_data.Rmd
amend T-crit value in 03_prep_data.rmd and re-Knit all subsequently effected files
Edit 03_Prep_data, lets to lets, clean up code chunks, etc.

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq())
```

```{r import_data}
PM_MB_means <- read.csv("cache/1911_PM_MB_means&Ygains.csv")

source("R/same.R") # matches each element of a vector and does not return NAs
```

@@

```{r LSD_2_Sampling_Variance}
Tcrit <- 1.697 # 0.05 and DFw = 30

@@

>>>>

```{r load_libraries, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq()
)
```

```{r import_data}
PM_MB_means <- read.csv(here("cache/1911_PM_MB_means&Ygains.csv"))

source(here("R/same.R")) # matches each element of a vector and does not return NAs
```

@@

```{r LSD_2_Sampling_Variance}
Tcrit <- 2.042 # 0.05 and DFw = 30

@@

### Mungbeans age and yield saved

The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
Let's have a look at the age of each trial when each powdery mildew infected it.
We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity.

```{r age_andYield}
dat1 <- slimmer_PM_dat %>%
   mutate(days2PM = first_sign_disease - planting_date) %>%
   arrange(desc(days2PM)) %>%
   select(
      trial_ref,
      year,
      location,
      spray_management,
      days2PM,
      grain_yield.t.ha,
      yield_gain,
      prop_yield_gain,
      AUDPC_m,
      D_pres,
      PM_final_severity
   )
dat1
```

From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
Therefore I will not inspect, `AM1304` (Marys Mount).

We can see that the crops which were likely the most mature, did not show large yield gains, in particular:

   * Hermitage 2019  
   * Premer  
   * Goolhi  
   * Millmerran

Let's look at this in a quick box plot. 
We will only look at trials where powdery mildew set in at flowering which is approximately 60 days after planting.

```{r ageBoxPlot}
dat1 %>%
   filter(days2PM >= 60) %>%
   filter(spray_management != "control" &
             trial_ref != "AM1304") %>%
   group_by(trial_ref, spray_management) %>%
   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
   geom_boxplot() +
   geom_hline(yintercept = 0)
```

We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application.

For completeness let's test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.

```{r PM40_2_59_days}
dat1 %>%
   filter(days2PM < 60 &
             days2PM >= 40) %>%
   filter(spray_management != "control") %>%
   group_by(trial_ref, spray_management) %>%
   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
   geom_boxplot() +
   geom_hline(yintercept = 0)
```

We can see here all four experiments benefited, on average, from more than one spray.

Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_means` which include some observations of crop maturity.

```{r whatAreTheAges}
dat2 <- PM_MB_means %>%
   mutate(
      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
   ) %>%
   select(location, year, flower, pod, late_pod) %>%
   distinct() %>%
   arrange(desc(flower))

index1 <-
   apply(dat2, 1 , function(X)
      ! all(is.na(X[c("flower", "pod", "late_pod")])))

dat2[index1, ]
as.double(mean(dat2[index1, "flower"], na.rm = TRUE))
as.double(mean(dat2[index1, "pod"], na.rm = TRUE))
as.double(mean(dat2[index1, "late_pod"], na.rm = TRUE))
```

We can see that flowering and podding can be variable, and depend on the cumulative degree days.
However, on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`.
